---
title: "Report on New Zealand maize management online survey"
output:
  word_document: default
  html_document: default
---
> ----------------------

## 1. Background

New Zealand maize growers in the FAR database were contacted by email in August 2015 and asked to contribute to an online survey on crop management and yields (see last section).

The main aim of the survey was to provide a nationwide overview of crop performance and the most common management practices currently utilized in New Zealand. The data was used to develop a prototype model, recently concluded, able to estimate regional differences in crop yields across the entire country (Figure 1).

This report highlights the key insights gained from the survey data with responses from 106 maize growers across New Zealand.


```{r Libs, echo=FALSE, include=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(lubridate)
library(maps)
library(ggmap)
library(ggthemes)
library(readxl)
library(GGally)
```



```{r LoadData, echo=FALSE, include=FALSE}

setwd("\\\\Lin-file\\home$\\Cfleit\\My Documents\\Projects\\2015_MaizeSurveyFAR\\Analysis")
getwd()

data_clean <- read.table("DataCleanAndWorked.txt",header=TRUE) %>%
  mutate(RegionName = ifelse(RegionName=="HawkesBay", "Hawke's Bay", 
         ifelse(RegionName=="BayofPlenty", "Bay of Plenty", 
         as.character(RegionName)))) 

head(data_clean)
summary (data_clean)

```

## 2. Survey results

The map shows the "aproximate" location of respondents (actual locations were slighly modified to ensure anonymity of responses). 


```{r, echo = FALSE}
info_raw <- read.csv("C:/GitHubRepos/MaizeSurvey/CoordRespRegion.csv", header = TRUE)

sites <- info_raw %>%
  mutate(region = ifelse(region=="HawkesBay", "Hawke's Bay", 
         ifelse(region=="BayofPlenty", "Bay of Plenty", 
         as.character(region)))) %>%
  mutate(region=factor(region))

if (require("maps")) {
  # Create a lat-long dataframe from the maps package
  nz <- map_data("nz")
  # Prepare a plot of the map
  nzmap <- ggplot(nz, aes(x = long, y = lat, group = region)) +
    geom_polygon(fill = "white", colour = "black")
  
  # Plot it in cartesian coordinates
  nzmap
  # With correct mercator projection
  nzmap + coord_map()
  # With the aspect ratio approximation
  nzmap + coord_quickmap()+geom_point(data = sites, aes(x=long, y=lat, group = region, color = region), shape = 21,size=2, alpha=.9) + ylab("Latitude") + xlab("Longitude")
}
```

Figure 1. Map with approximate location, slightly modified to ensure anonymity, of the 106 respondents of the survey about maize management across New Zealand.

> ----------------------

More than half of the responses came from the Waikato and Canterbury regions (Figure 2).

```{r General, echo=FALSE, fig.height=7, fig.width=12}

#bar 
# data_clean %>%
#   group_by(RegionName) %>%
#   summarise(count = n()) %>%
#   mutate(RegionName =  reorder(RegionName, count)) %>%
#   ggplot(aes(x=RegionName, y=count)) +
#   geom_bar(stat="identity") +
#   ylab("Number of respondents") + 
#   theme(axis.text.x = element_text(angle = 90))



# Simple Pie Chart
slices <- data_clean %>%
  group_by(RegionName) %>%
  summarise(obsCount = n()) %>%
  mutate(prc = round((obsCount/sum(obsCount))*100),2) %>% 
  na.omit() # Dave Saville suggestion of not including non-respondents 

lbls <- paste0(slices$RegionName," (",slices$prc,"%)")
pie(slices$obsCount, labels = lbls, cex=1.5, main="Regions")


# ggsave(file=paste0("Fig_ANOVA_SS_",methodCalc[met], ".tiff"), dpi = 300)


```

Figure 2. Percentage of survey responses per region.

> ----------------------

More than 70% of respondents had main areas of maize in elevations <200 m above sea level (Figure 3).

```{r Altitude, echo=FALSE,fig.height=7, fig.width=12, warning=FALSE}

#bar 
# data_clean %>%
#  # filter(- is.na(Altitude_m_asl)==TRUE) %>%
#   group_by(Altitude_m_asl) %>%
#   summarise(obsCount = n()) %>%
#  # mutate(Altitude_m_asl =  reorder(Altitude_m_asl, obsCount)) %>%
#   ggplot(aes(x=Altitude_m_asl, y=obsCount)) +
#   geom_bar(stat="identity") +
#   xlab("Altitude above sea level (m)") +
#   ylab("Number of producers")  +
#   coord_flip()
#unique(data_clean$Altitude_m_asl)

slices <- data_clean %>%
  group_by(Altitude_m_asl) %>%
  summarise(obsCount = n()) %>%
  mutate(prc = round((obsCount/sum(obsCount))*100),2) %>% 
  na.omit() %>%
  ungroup() %>%
  # Dave Saville suggestion of not including non-respondents
  mutate(Altitude_m_asl = factor(Altitude_m_asl, 
                                 levels=c(0,30, 76, 151, 251, 400, 500),
                                 labels=c("0","10-50","51-100" ,"101-200", "201-300","301-500",">500 ")
                                 )) 

lbls <- paste0(slices$Altitude_m_asl," m (",slices$prc,"%)")
pie(slices$obsCount, labels = lbls, cex=1.5, main="Elevation of main production areas (m)")

```

Figure 3. Distribution of survey respondents by altitude category.

> ----------------------

Most of the respondents have grown maize for more than 10 years (Figure 4).

```{r YearsAsProducer, echo=FALSE,fig.height=7, fig.width=12}

# Simple Pie Chart
slices <- data_clean %>%
  group_by(YearsAsProducer) %>%
  summarise(obsCount = n()) %>%
  mutate(prc = round((obsCount/sum(obsCount))*100),2) %>%
  na.omit() %>%
  ungroup() %>%
  # Dave Saville suggestion of not including non-respondents
  mutate(YearsAsProducer = factor(YearsAsProducer, 
                                 levels=c(2,4, 8, 11),
                                 labels=c("<2","2 to 5",
                                          "6 to 10" ,">10")
                                 )) 

lbls <- paste0(slices$YearsAsProducer," years (",slices$prc,"%)")
pie(slices$obsCount, labels = lbls, cex=1.5, main="Years in maize silage production")

```

Figure 4. Distribution of survey respondents by years as a grower.

> ----------------------

Most of the respondents use conventional cultivation methods (Figure 5).

```{r CultivationType, echo=FALSE,fig.height=7, fig.width=12}

# Simple Pie Chart
slices <- data_clean %>%
  group_by(CultivationType) %>%
  summarise(obsCount = n()) %>%
  mutate(prc = round((obsCount/sum(obsCount))*100),2)

lbls <- paste0(slices$CultivationType," cultivation (",slices$prc,"%)")
pie(slices$obsCount, labels = lbls, cex=1.5, main="Cultivation method")

```

Figure 5. Distribution of survey respondents by cultivation method.

> ----------------------

Most of the reported cropping areas in the North Island did not use irrigation (Figure 6). Canterbury showed the highest percentage of irrigation areas.

```{r Irrigation, echo=FALSE,fig.height=5, fig.width=8}

#bar 
data_clean %>%
  group_by(RegionName) %>%
  summarise(obsCount = n(),irrig = mean(IrrigatedPercent), Latitude=mean(Latitude),
            mn = quantile(IrrigatedPercent, 0.25),
            mx = quantile(IrrigatedPercent, 0.75)) %>%
 # mutate(RegionName =  reorder(RegionName, Latitude)) %>%
  mutate(RegionName =  reorder(RegionName, irrig)) %>%
  ggplot(aes(x=RegionName, y=irrig)) +
  geom_bar(stat="identity") +
  coord_flip()  +
  ylab("Percentage irrigated area") +
  xlab("Region")+
  geom_text(aes(label = paste0("n=",obsCount), y = irrig+5))


```

Figure 6. Average percentage of maize acreage under irrigation per grower by region. Calculation assumes mid-points of acreage for each category with a maximum area of 100 ha. The value of n is the number of respondents per region.

> ----------------------

The percentage of total reported areas in silage ranged from zero in Gisborne to 100% in Taranaki (Figure 7).

```{r SilageArea, echo=FALSE,fig.height=5, fig.width=8}
data_clean %>%    
  mutate(region=factor(RegionName)) %>%
  group_by(RegionName) %>%
   summarise(obsCount = n(),sil = mean(SilagePercent), Latitude=mean(Latitude),
            mn = quantile(SilagePercent, 0.25),
            mx = quantile(SilagePercent, 0.75)) %>%
 # mutate(RegionName =  reorder(RegionName, Latitude)) %>%
  mutate(RegionName =  reorder(RegionName, sil)) %>%
  ggplot(aes(x=RegionName, y=sil)) +
  geom_bar(stat="identity") +
  coord_flip() +
  ylab("Percentage silage area")+
  xlab("Region")+
  geom_text(aes(label = paste0("n=",obsCount), y = sil+5))#  +
 #  geom_errorbar(aes(ymax = mx, ymin = mn), 
              #   position=position_dodge(width=0.9), width=0.25)
```

Figure 7. Average percentage of maize acreage as silage per grower by region. Calculation assumes mid-points of acreage for each category with a maximum area of 100 ha. The value of n is the number of respondents per region.

> ----------------------

The range in sowing dates, for early-, Most frequently experienced and late-sowing conditions, is shown in Figure 8.

```{r sowDate, echo=FALSE, warning=FALSE,fig.height=10, fig.width=8, include = FALSE}

# in facets
data_clean %>%
  dplyr::select(RegionName, EarlySowAdj, AverageSowAdj,LateSowAdj) %>%
  tidyr::gather("Category","value", 2:4) %>%
  mutate(RegionName =  reorder(RegionName, value)) %>%
  mutate(value = parse_date_time(as.character(value),"j")) %>%
  ggplot(aes(x=RegionName, y=value)) +
  geom_boxplot(aes(alpha=0.2)) +
  geom_jitter(aes(colour=Category)) +
  facet_grid(Category~.) + # Comment out for a single graph
  coord_flip() + theme(legend.position="none") +
  ylab("Sowing dates")


```



```{r, fig.height=6, fig.width=12, warning = FALSE, echo=FALSE}
data_clean %>%
  dplyr::select(RegionName, EarlySowAdj, AverageSowAdj,LateSowAdj) %>%
  tidyr::gather("Category","value", 2:4) %>%
  mutate(RegionName =  reorder(RegionName, value)) %>%
  mutate(value = parse_date_time(as.character(value),"j")) %>%
  mutate(Category = factor(Category,
                           levels=c("EarlySowAdj",
                                    "AverageSowAdj",
                                    "LateSowAdj"), 
                           labels=c("Early sowing","Most frequent","Late sowing") )) %>%
  ggplot(aes(x=RegionName, y=value)) +
#  geom_boxplot(alpha=0.2) +
 # geom_jitter( width = 0.1, alpha = 0.5, size = 2, shape = 1) +
#  scale_shape_discrete(solid=F) +
#  geom_line(size=2, alpha=0.5, aes(colour=Category)) +
    # geom_jitter( width = 0.1, 
    #            alpha = 0.5,
    #            size = 2, 
    #            shape = 1,
    #            aes(colour=Category)) +
  geom_point(aes(colour=Category),
             shape = 21, alpha = 0.8, size =3, 
             position=position_jitterdodge(dodge.width = 0.5)) +
  scale_shape_discrete(solid=F) +  
  geom_line(size=4, alpha=0.3, 
            aes(colour=Category),
            position = position_dodge(width = 0.5)) +
  theme(legend.position="top") +
  theme(legend.title=element_blank())+
  coord_flip() + 
  # theme(legend.position="none") +
  ylab("Sowing dates") +
  theme(text=element_text(size=18)) +
  xlab("Region name")
```

Figure 8. Most frequently experienced, early- and late-sowing dates reported by respondents per region. Points are individual responses and lines indicate range of responses. Calculation assumes mid-points of sowing date for each category.

> ----------------------

```{r,echo=FALSE, warning=FALSE,fig.height=6, fig.width=12, include = FALSE}
data_clean %>%
  dplyr::select(ClimateZone, EarlySowAdj, AverageSowAdj,LateSowAdj) %>%
  tidyr::gather("Category","value", 2:4) %>%
  mutate(RegionName =  reorder(ClimateZone, value)) %>%
  mutate(value = parse_date_time(as.character(value),"j")) %>%
  mutate(Category = factor(Category,
                           levels=c("EarlySowAdj",
                                    "AverageSowAdj",
                                    "LateSowAdj"), 
                           labels=c("Early sowing","Most frequent","Late sowing") )) %>%
  ggplot(aes(x=ClimateZone, y=value)) +
  geom_violin(alpha=0.2) +
  geom_jitter(aes(colour=Category), width = 0.2, alpha = 0.5, size = 2) +
 # facet_grid(Category~.) + # Comment out for a single graph
  coord_flip() + 
  # theme(legend.position="none") +
  ylab("Sowing dates") +
  theme(text=element_text(size=18)) +
  xlab("Region name")
```

The Most frequent factor that delay sowing date was excessive soil moisture in spring, with the exception of Canterbury where low temperatures (including risks of frost) was the main delay factor (Figure 9).

```{r DelaySowFact, echo=FALSE,fig.height=4, fig.width=8}

#bar 
data_clean %>%
  dplyr::select(RegionName, ColdTemp, WetSoil, DrySoil, NoMachine, FrostRisk) %>%
  mutate(LowTemp=ColdTemp+FrostRisk, Others=NoMachine+DrySoil) %>%
  dplyr::select(-ColdTemp,-FrostRisk,-DrySoil,-NoMachine) %>%
#  tidyr::gather("DelayFactor","n", 2:6) %>%
  tidyr::gather("DelayFactor","n", WetSoil:Others) %>%
#  mutate(DelayFactor =  reorder(DelayFactor, n)) %>%
  mutate(DelayFactor =  factor(DelayFactor, 
                               levels=c("WetSoil","LowTemp","Others"), 
                               label=c("Wet Soil","Low Temperatures","Other factors"))) %>%
  ggplot(aes(x=RegionName, y=n)) +
  geom_bar(stat="identity") +
  coord_flip() +
  facet_wrap(~DelayFactor, ncol=6) +
  xlab("Factors that delay sowing date") +
  ylab("Number of respondents") 

```

Figure 9. Main factors contributing to a delay in the time of maize sowing. Number of producers that selected each category. "Low temperatures" category includes frost risk and low soil temperatures. The category "others" includes lack of available machinery and very dry soil conditions.

> ----------------------

The minimum and maximum Comparative Relative Maturity (CRM) reported gave an indication of the range of hybrid maturities selected by growers in each region (Figure 10).


```{r CRM, echo=FALSE, warning=FALSE,fig.height=6, fig.width=12}

# FIXME: Saville suggested using the common rare info explicitly

#bar 
# data_clean %>%
#   dplyr::select(RegionName, CRM_max, CRM_min) %>%
#   tidyr::gather("CRMcat","value", 2:3) %>%
#   mutate(CRMcat = as.factor(CRMcat)) %>%
#   mutate(RegionName =  reorder(RegionName, value)) %>%
#   #group_by(RegionName, CRMcat) %>%
#  # summarise(value = mean(na.exclude(value))) %>%
#   ggplot(aes(x=RegionName, y=value)) +
#   geom_boxplot(aes(alpha=0.1)) +
#   coord_flip() +
#   facet_grid(CRMcat~.)+
#   geom_jitter(aes(colour=RegionName)) +
#   ylab("CRMs") +
#   xlab("Region") + theme(legend.position="none")

data_clean %>%
  dplyr::select(RegionName, CRM_max, CRM_min) %>%
  tidyr::gather("Category","value", CRM_min:CRM_max) %>%
  mutate(RegionName =  reorder(RegionName, value)) %>%
  mutate(Category = factor(Category,
                           levels=c("CRM_min",
                                    "CRM_max"), 
                           labels=c("Early maturity choice","Late maturity choice") )) %>%
  ggplot(aes(x=RegionName, y=value)) +
#  geom_boxplot(alpha=0.2) +
#  geom_jitter(aes(colour=Category), width = 0.2, alpha = 0.5, size = 2) +
  # geom_jitter( width = 0.1, 
  #              alpha = 0.5,
  #              size = 2, 
  #              shape = 1,
  #              aes(colour=Category)) +
    geom_point(aes(colour=Category),
             shape = 21, alpha = 0.8, size =3,
             position=position_jitterdodge(dodge.width = 0.5)) +
  scale_shape_discrete(solid=F) +  
  geom_line(size=4, alpha=0.5, aes(colour=Category),position = position_dodge(width = 0.5)) +
#  facet_grid(Category~.) + # Comment out for a single graph
  coord_flip() + 

    theme(legend.position="top") +
  theme(legend.title=element_blank())+
  ylab("Comparative Relative Maturity (CRM)") +
  theme(text=element_text(size=18)) +
  xlab("Region name")

```

Figure 10. Range of hybrid maturity selection based on Comparative Relative Maturity (CRM). Maximum and minimum CRM values selected by respondents were classified as early- and late-maturity choices for a given region. Points are individual responses and lines indicate range of responses. Calculation assumes mid-points of CRM categories for both commonly used and less frequently used hybrid maturities.

> ----------------------

```{r, include = FALSE,echo=FALSE}
#bar 
data_clean %>%
  dplyr::select(RegionName, CRM_max, CRM_min) %>%
  tidyr::gather("CRMcat","value", 2:3) %>%
  mutate(CRMcat = as.factor(CRMcat)) %>%
  mutate(RegionName =  reorder(RegionName, value)) %>%
  #group_by(RegionName, CRMcat) %>%
 # summarise(value = mean(na.exclude(value))) %>%
  ggplot(aes(x=RegionName, y=value)) +
  geom_boxplot(alpha=0.1) +
  coord_flip() +
#  facet_grid(CRMcat~.)+
  geom_jitter(aes(colour=RegionName), width = 0.2) +
  ylab("Maize hybrid maturity rate (early to late-maturity)") +
  xlab("Region")  + theme(legend.position="none")

```



```{r SilageYield, echo=FALSE, warning=FALSE, fig.height=10, fig.width=8, include = FALSE}

data_clean %>%
  dplyr::select(RegionName, Silage_Yield_Low_Adj, Silage_Yield_Med_Adj,Silage_Yield_High_Adj) %>%
  tidyr::gather("Category","value", 2:4) %>%
 # mutate(CRMcat = as.factor(CRMcat)) %>%
  mutate(RegionName =  reorder(RegionName, value)) %>%
  #group_by(RegionName, CRMcat) %>%
 # summarise(value = mean(na.exclude(value))) %>%
  ggplot(aes(x=RegionName, y=value)) +
 # geom_boxplot(aes(alpha=0.5)) +
  coord_flip() +
  facet_grid(Category~.) +
  geom_jitter(aes(alpha=0.8, shape  = RegionName, colour=RegionName)) + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0))  + 
  theme(legend.position="top") +
  ylab(" Silage yield (t/ha)") + theme(legend.position="none")
```

The yields for silage (Figure 11) and grain (Figure 12) maize were classified into low-yielding years, average years and high-yielding years.

```{r, fig.height=6, fig.width=12, warning = FALSE, echo=FALSE, include = FALSE}
data_clean %>%
  dplyr::select(RegionName, Silage_Yield_Low_Adj, Silage_Yield_Med_Adj,Silage_Yield_High_Adj) %>%
  tidyr::gather("Category","value", 2:4) %>%
 # mutate(CRMcat = as.factor(CRMcat)) %>%
  mutate(Category = factor(Category,
                           levels=c("Silage_Yield_Low_Adj",
                                    "Silage_Yield_Med_Adj",
                                    "Silage_Yield_High_Adj"), 
                           labels=c("Low-yielding years","Common yields","High-yielding years") )) %>%
  mutate(RegionName =  reorder(RegionName, value)) %>%
  #group_by(RegionName, CRMcat) %>%
 # summarise(value = mean(na.exclude(value))) %>%
  ggplot(aes(x=RegionName, y=value)) +
#    geom_line(size=4, alpha=0.5, aes(colour=Category),position = position_dodge(width = 0.5)) +
    # geom_jitter( width = 0.1, 
    #            alpha = 0.5,
    #            size = 2, 
    #            shape = 1,
    #            aes(colour=Category)) +
#  scale_shape_discrete(solid=F) +  
  geom_boxplot(alpha=0.5, width=0.5) +
  coord_flip() +
#  facet_grid(Category~.) +
  geom_jitter(aes(colour=factor(Category)), alpha=0.5, width=0.1) + 
  scale_colour_discrete(name="Category") +
 # theme(legend.position="top") +
  theme(text = element_text(size=20)) +
  xlab("Region Name")  + 
  ylab("Silage yield (t/ha)") # + 
 # theme(legend.position="none")

# FIXME: do histogram with facet wrap by region using actual categories

```


```{r, fig.height=6, fig.width=12, warning = FALSE, echo=FALSE}
data_clean %>%
  dplyr::select(RegionName, Silage_Yield_Low_Adj, Silage_Yield_Med_Adj,Silage_Yield_High_Adj) %>%
  tidyr::gather("Category","value", 2:4) %>%
 # mutate(CRMcat = as.factor(CRMcat)) %>%
  mutate(Category = factor(Category,
                           levels=c("Silage_Yield_Low_Adj",
                                    "Silage_Yield_Med_Adj",
                                    "Silage_Yield_High_Adj"), 
                           labels=c("Low-yields","Most frequent yields","High-yields") )) %>%
  mutate(RegionName =  reorder(RegionName, value)) %>%
  ggplot(aes(x=RegionName, y=value)) +
#  scale_shape_discrete(solid=F) +  
  geom_line(size=4, alpha=0.3, aes(colour=Category),position = position_dodge(width = 0.7)) +
  geom_point(aes(colour=Category),
             shape = 21, alpha = 1, size =3,
             position=position_jitterdodge(dodge.width = 0.7)) +
# scale_shape_discrete(solid=F) +
  coord_flip() +
#  scale_colour_discrete(name="Category") +
#  theme(legend.position="top") +
  theme(text = element_text(size=20)) +
  theme(legend.position="top") +
  theme(legend.title=element_blank())+
  xlab("Region Name")  + 
  ylab("Silage yield (t/ha)") # + 
 # theme(legend.position="none")
```


```{r, waring=FALSE, include=FALSE}

# Try using a hystogram as suggested by David Saville

silagecat <- c("<10","10 to 15","15 to 17","18 to 22","23 to 26","27 to 30",">30")
silageVals <- c(8,13,16,20,25,29,32)
grainCat <- c("<5","5 to 7","8 to 10","11 to 13","14 to 16",">16")
grainVals <- c(3,6,9,12,15,18)

data_clean %>%
  mutate(Silage_Yield_Low_Adj = factor(Silage_Yield_Low_Adj, levels=silageVals,labels=silagecat)) %>%
  mutate(Silage_Yield_Med_Adj = factor(Silage_Yield_Med_Adj, levels=silageVals,labels=silagecat)) %>%
  mutate(Silage_Yield_High_Adj = factor(Silage_Yield_High_Adj, levels=silageVals,labels=silagecat)) %>%
  dplyr::select(RegionName, Silage_Yield_Low_Adj, Silage_Yield_Med_Adj,Silage_Yield_High_Adj) %>%
  tidyr::gather("Category","value", Silage_Yield_Low_Adj:Silage_Yield_High_Adj) %>%
  # mutate(value = factor(value, # make it category again to do hystogram
  #                       levels=c(),
  #                       labels=c()
  #                       
  #                       )) %>%
 # mutate(CRMcat = as.factor(CRMcat)) %>%
  mutate(Category = factor(Category,
                           levels=c("Silage_Yield_Low_Adj",
                                    "Silage_Yield_Med_Adj",
                                    "Silage_Yield_High_Adj"), 
                           labels=c("Low-yielding years","Common yields","High-yielding years") )) %>%
  #  mutate(RegionName =  reorder(RegionName, value)) %>%
  #  group_by(RegionName, CRMcat) %>%
  #  summarise(value = mean(na.exclude(value))) %>%
  na.omit() %>%
  ggplot(aes(x=value)) +
  geom_histogram(stat='count',aes(fill = Category)) +
#  geom_histogram(subset(Category == 'Low-yielding years'),fill = "red", alpha = 0.2,stat='count') +
#  geom_histogram(subset(Category == 'Common yields'),fill = "blue", alpha = 0.2,stat='count') +
#  geom_histogram(subset(Category == 'High-yielding years'),fill = "green", alpha = 0.2,stat='count') +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  facet_wrap(~RegionName)
#    geom_line(size=4, alpha=0.5, aes(colour=Category),position = position_dodge(width = 0.5)) +
    # geom_jitter( width = 0.1, 
    #            alpha = 0.5,
    #            size = 2, 
    #            shape = 1,
    #            aes(colour=Category)) +
#  scale_shape_discrete(solid=F) +  

 # geom_boxplot(alpha=0.5, width=0.5) +
 # coord_flip() +
#  facet_grid(Category~.) +
#  geom_jitter(aes(colour=factor(Category)), alpha=0.5, width=0.1) + 
 # scale_colour_discrete(name="Category") +
 # theme(legend.position="top") +
#  theme(text = element_text(size=20)) +
#  xlab("Region Name")  + 
 # ylab("Silage yield (t/ha)") # + 
 # theme(legend.position="none")

# FIXME: do histogram with facet wrap by region using actual categories
```

Figure 11. Distribution of silage maize yields per region. Boxes show quantile distributions or ranges. Calculation assumes mid-points of CRM categories.

> ----------------------



```{r, fig.height=6, fig.width=12, warning = FALSE, echo=FALSE, include = FALSE}
data_clean %>%
  dplyr::select(RegionName, Grain_Yield_Low_Adj, Grain_Yield_Med_Adj,Grain_Yield_High_Adj) %>%
  tidyr::gather("Category","value", 2:4) %>%
 # mutate(CRMcat = as.factor(CRMcat)) %>%
  mutate(Category = factor(Category,
                           levels=c("Grain_Yield_Low_Adj",
                                    "Grain_Yield_Med_Adj",
                                    "Grain_Yield_High_Adj"), 
                           labels=c("Low-yielding years","Common yields","High-yielding years") )) %>%
  mutate(RegionName =  reorder(RegionName, value)) %>%
  #group_by(RegionName, CRMcat) %>%
 # summarise(value = mean(na.exclude(value))) %>%
  ggplot(aes(x=RegionName, y=value)) +
  geom_boxplot(alpha=0.5, width=0.5) +
  coord_flip() +
 # facet_grid(Category~.) +
  geom_jitter(aes(colour=factor(Category)), alpha=0.5, width=0.1) + 
  scale_colour_discrete(name="Category") +
 # theme(legend.position="top") +
  theme(text = element_text(size=20)) +
  xlab("Region Name")  + 
  ylab("Grain yield (t/ha)") # + 
 # theme(legend.position="none")

```

```{r, fig.height=6, fig.width=12, warning = FALSE, echo=FALSE}
data_clean %>%
  dplyr::select(RegionName, Grain_Yield_Low_Adj,
                                    Grain_Yield_Med_Adj,
                                    Grain_Yield_High_Adj) %>%
  tidyr::gather("Category","value", 2:4) %>%
 # mutate(CRMcat = as.factor(CRMcat)) %>%
  mutate(Category = factor(Category,
                           levels=c("Grain_Yield_Low_Adj",
                                    "Grain_Yield_Med_Adj",
                                    "Grain_Yield_High_Adj"), 
                           labels=c("Low-yields","Most frequent yields","High-yields") )) %>%
  mutate(RegionName =  reorder(RegionName, value)) %>%
  ggplot(aes(x=RegionName, y=value)) +
#  scale_shape_discrete(solid=F) +  
  geom_line(size=4, alpha=0.3, aes(colour=Category),position = position_dodge(width = 0.7)) +
  geom_point(aes(colour=Category),
             shape = 21, alpha = 1, size =3, 
             position=position_jitterdodge(dodge.width = 0.7)) +
# scale_shape_discrete(solid=F) +
  coord_flip() +
#  scale_colour_discrete(name="Category") +
  theme(legend.position="top") +
  theme(legend.title=element_blank())+
  theme(text = element_text(size=20)) +
  xlab("Region Name")  + 
  ylab("Silage yield (t/ha)") # + 
 # theme(legend.position="none")
```

Figure 12. Distribution of grain maize yields reported by respondents per region. Boxes show 25th and 75th percentile central line is the median value.Calculation assumes mid-points of CRM categories.


The information from this survey was used to parameterise the APSIM model for national-scale assessments of crop yield. For example, Figure 13 shows categories of simulated silage yield based on the ranges of sowing dates and hybrids from the survey.

![Figure 13. Silage yield simulation categories by APSIM-maize and approximate survey respondent regions.](Respondents_YieldCat.tiff)


> ----------------------

## 3. Summary

Additional insights from this survey include:

- Sowing dates and genotype maturities were widely variable, even within each regions
- Wet soil was the Most frequent factor delaying sowing of maize crops
- Most maize growers utilise conventional cultivation methods
- Silage yields were on average ~20 t/ha; mostly ranging between 15 and 25 t/ha
- Grain yields were on average ~12 t/ha; mostly ranging between 9 and 15 t/ha


## Acknowledgements
We sincerely thank the maize producers who contributed to this survey. We thank David Saville for invaluable support in the analyses of the survey data.